Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-04 main.tex
Some notes on StkTokens' ESOP predecessor

>>>>

  In their ESOP 2018 paper, the same authors present a similar scheme that uses
  local capabilities employing similar techniques. Their capability machine is
  mostly standard. Operations other than those working on capabilities are
  mostly standard, with small extensions to account for the presence
  capabilities. Notably, jmp needs to account for enter capabilities, which can
  only be used to jump to a location and then become read-execute; they
  represent an opaque packing of some code together with local state. The store
  operation is also complicated, this time by the presence of local
  capabilities, which can only be stored in registers (and write-local memory)
  and may be temporarily handed over to an adversary, say for the duration of a
  call.

  The work presents a concrete calling convention that relies on a single shared
  stack and has moderate overhead with stack and return pointers passed through
  registers as local capabilities. The scheme imposes some standard conditions
  on initial state and memory allocation primitives, and safety measures a
  component needs to perform to protect itself against an adversary. The most
  demanding requirement is that not only non-return value registers and used
  stack, but also the unused part of the stack (which may contain local
  capabilities) needs to be cleared when returning to the adversary. Simple
  measures are applied on calls and returns to and from an adversary, and on
  calls from an adversary.

  The logical relation that is presented is not specific to the particular
  calling convention. It uses a variant of the public-private separation of
  worlds to model the particular properties of local capabilities. In
  particular, worlds have permanent, temporary and revoked regions, with
  non-revoked regions comprising a state transition system with both public and
  private transitions. Local and global capabilities can depend on protocols
  from permanent regions, and local capabilities can also depend on protocols
  from temporary regions (which may be revoked in the future, and may not
  outlive those regions). A pair of future world relations describe the changes
  of memory over time. In the public FW relation, temporary and permanent
  regions can evolve according to the public part of their transition system,
  and revoked regions can be reinstated as temporary. In the private FW
  relation, temporary and revoked regions can be replaced by arbitrary regions,
  and permanent regions can evolve according to the private part of their
  transition system. The relation defines an observation relation for safe
  configurations (i.e., the memory of a halting configuration is satisfied by
  some private FW). The relation on values covers conditions for the safe use of
  write and write-local capabilities, and similarly for enter capabilities.

  All this is used to prove WBCF and LCE for concrete example programs.
